Innovation and elaboration on the avian tree of life - supplementary materials

### 2023-05-11 Manuscript/supplementaries.tex
Update supplementaries.tex

\begin{figure}[htpb]
\centering
\centering
   \includegraphics[width=0.5\textwidth]{Figures/correlations_fable.pdf}
\caption{Posterior distributions of the correlations scores between $elaboration_{species}$ and $innovation_{species}$ as displayed for each super-orders in Fig. \ref{Fig:figure_correlations}. Species' projection onto the whole phylogeny's major axis of phenotypic variance-covariance (VCV) corresponds to the correlation scores for the panels A and B in Fig. \ref{Fig:figure_correlations} and species' projections onto their own super-order's major axis of phenotypic variance-covariance (VCV) corresponds to the correlation scores for the panel C in Fig. \ref{Fig:figure_correlations}}
\label{Fig:fable_correlations}
\end{figure}

>>>>

\begin{figure}[htpb]
\centering
\centering
   \includegraphics[width=0.5\textwidth]{Figures/correlations_fable.pdf}
\caption{Posterior distributions of the correlations scores between $elaboration_{species}$ and $innovation_{species}$ as displayed for each super-orders in Fig. \ref{Fig:figure_correlations}. Species' projection onto the whole phylogeny's major axis of phenotypic variance-covariance (VCV) corresponds to the correlation scores for the panels A and B in Fig. \ref{Fig:figure_correlations} and species' projections onto their own super-order's major axis of phenotypic variance-covariance (VCV) corresponds to the correlation scores for the panel C in Fig. \ref{Fig:figure_correlations}.}
\label{Fig:fable_correlations}
\end{figure}

\begin{figure}[htpb]
\centering
\centering
   \includegraphics[width=0.5\textwidth]{Figures/Elaboration_and_innovation_through_time.pdf}
\caption{Distribution of $elaboration_{clade}$ and $innovation_{clade}$ for each order and super-order through time. Refer to the colours in Fig. 3 in the main text for the names of each order and super-order plotted.}
\end{figure}
